---
title: "Develop Data Products Week2"
author: "Benjamin Mohn"
date: "01.16.2019"
output: html_document
---

## R Markdown

This R-Markdown document was created in order to Fullfill the assignment of the Developing Data Producte for Week 2.  

Structure is, at first general information of this document are presented. Such as date, information about the map. Secondly the map is beeing shown.

## Information
This Markdown file was created on the **16th of January 2019** by **Benjamin Mohn**.

The map is showing germany and some of the most famous sights one can now such as: 

1. Brandenburger Tor (Berlin)
2. Fernsehturm (Berlin)
3. Reeperbahn (Hamburg)
4. Schloss Neuschwanstein (Bayern)
5. Brocken (Sachen Anhalt)
6. Koelner Dom (Nordrhein-Westfalen)
7. Gespenster Wald Nienhagen (Mecklenburg-Vorpommern)
8. Zeche Zollberein (Nordrhein-Westfalen)
```{r libraries, echo=FALSE}
library(leaflet)
```

```{r points_info}
point_df <- data.frame('lat' = c(52.516231, 
                                 52.520803, 
                                 53.549853, 
                                 47.557610, 
                                 51.799742,
                                 50.941326,
                                 54.162779,
                                 51.490034),
                       'lng' = c(13.377724,
                                 13.409269,
                                 9.965406,
                                 10.749597,
                                 10.615730,
                                 6.957722,
                                 11.940504,
                                 7.041685))
popups <- c('Brandenburger Tor (Berlin)',
            'Fernsehturm (Berlin)',
            'Reeperbahn (Hamburg)',
            'Schloss Neuschwanstein (Bavaria)',
            'Brocken (Saxony-Anhalt)',
            'Koelner Dom (North Rhine-Westphalia)',
            'Gespenster Wald Nienhagen (Mecklenburg-Vorpommern)',
            'Zeche Zollberein (North Rhine-Westphalia)')
icons <- awesomeIcons(icon='camera',
                      iconColor = 'yellow',
                      markerColor='red')
```

```{r leaflet}
point_df %>% 
leaflet() %>% 
addProviderTiles(providers$Stamen.Toner) %>%
setView(lng = 10.478087, lat = 51.295872, zoom = 5) %>%
addAwesomeMarkers(popup=popups, icon=icons)
```